Quantum Hoare Types

### 2019-12-15 ms-paper/ms-paper.tex
Add John's suggestions, some minor bib updates

\subsection{Type Theory}
\textit{Basics of type theory for non-specialists\ldots}

\subsection{Program Proof}
\textit{Basics of program proof and techniques for non-specialists\ldots}

@@

@@

\subsection{Programming Languages for Quantum Computing}
\textit{A chronology of language developments\ldots}

@@

@@

\begin{acks}
	I would like to thank my advisor John Reppy for suggesting me to look at Hoare Type Theory that led to this master's thesis and for his constant support and encouragement to see it through. I also thank my committee members Fred Chong and Ravi Chugh for reading drafts of this document and providing useful feedback.

>>>>

\subsection{Hoare Style Reasoning}
\textit{Basics of Hoare-triples for non-specialists\ldots}

\subsection{Program Proof and HTT}
\textit{Basics of program proof and techniques for non-specialists\ldots}

\section{Running Example}
\textit{Move teleportation example here}

@@

\section{Evaluation}

\subsection{More Examples}
\textit{add at least one example with scaling knob}

\subsection{Circuit-complexity Considerations}

@@

\subsection{Quantum Languages and Types}
\textit{A chronology of language developments wrt to usefulness of types\ldots}

@@

\textit{Add from Mingsheng Ying's book, papers, etc.}

@@

\textit{Future work about using Proto-Quipper/\qwire as languages, then extraction into QASM and checking generated verification conditions.}

\begin{acks}
%	I would like to thank my advisor John Reppy for suggesting me to look at Hoare Type Theory that led to this master's thesis and for his constant support and encouragement to see it through. I also thank my committee members Fred Chong and Ravi Chugh for reading drafts of this document and providing useful feedback.
